---
title: 'Brand Equity Analysis: Moonshot Clinical Systems'
author: "Alice Lin"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Import the dataset and observe the data
```{r}
data = read.csv("moonshot.csv")
```

```{r}
library(dplyr) 
data_check = data %>%
  group_by(brand) %>%
  summarise(count = n(), 
            avg_nps = mean(nps),
            avg_sentiment = mean(sentiment),
            avg_intent = mean(intent))
data_check
```
**add box plot**

## 1. Determine Brand Equity Indicator

NPS, sentiment, and intent are all potential indicator to brand equity, so I would like to run some analysis to determine the best way to determine the dependent variable for the following analysis.

### Correlation Anaylsis
First of all, I ran a correlation analysis to check the relationship between 3 potential indicators. According to the result, there are moderate positive relationships between 3 potential indicators (all coefficients are greater than 0.5).
```{r}
data_DV = select(data, c(2:5))

data_DV %>%
  select(where(is.numeric)) %>%
  cor()
```
Used ANOVA to further understand the difference between 3 potential indicators and it looks like the differences between variables are either not significant or small enough to ignore.

### ANOVA
```{r}
library(scales)
library(tidyr)
data_rescale_DV = data_DV %>%
  mutate(sentiment = rescale(sentiment, to = c(1,5)))

data_rescale_DV_aov = data_rescale_DV %>% 
  select(where(is.numeric)) %>%
  pivot_longer(
    everything(),
    names_to = "DV",
    values_to = "value"
  ) 
a = aov(value ~ DV, data = data_rescale_DV_aov)

TukeyHSD(a)
  
```

Given the relationship between three variables, I considered to combine NPS, sentiment, and intent into a brand equity indicator and I ran a Chronbach’s Alpha to validate the idea.

### Chronbach’s Alpha / Alpha Reliability
```{r}
library(psych)

data_DV %>%
  select(where(is.numeric)) %>%
  psych::alpha()
```
The raw-alpha and std.alpha scores are both > 0.8, showing it’s better to consolidate the variables. Additionally, “Reliability if an item is dropped” statistics shows dropping either one of the variables will lower the alpha score, so I should consolidate all three variables.

### New Brand Equity Indicator
```{r}
data_rescale_DV = mutate(data_rescale_DV, brand_equity = (nps+sentiment+intent)/3)

brand_equity_stas = data_rescale_DV %>%
  group_by(brand) %>%
  summarise(avg_nps = mean(nps),
            avg_sentiment = mean(sentiment),
            avg_intent = mean(intent),
            avg_brand_equity = mean(brand_equity))

brand_equity_stas
```

The new brand equity indicator scales from 1~5. 

**add a bar chart**
